---
title: "extra eda snippets"
output: html_notebook
---

### Cross-validate baseline models
```{r}
# create nested data frame of full training data by key
num_keys <- length(unique(train$Primary_Key))
num_dates <- length(unique(train$Date))
train_full <- data.frame('Date' = rep(sort(unique(train$Date)), times = num_keys),
                         'Primary_Key' = rep(unique(train$Primary_Key), each = num_dates))
train_full <- left_join(train_full, train) %>%
  select(Date, Weekly_Sales, Primary_Key)
train_by_key <- train_full %>%
  group_by(Primary_Key) %>%
  nest

# get ts object for each key
get_ts_obj <- function(df) {
  ts_obj <- ts(df$Weekly_Sales, 
               freq=52, 
               start=lubridate::year(min(df$Date))+lubridate::yday(min(df$Date))/365.25)
}
train_by_key <- train_by_key %>% 
  mutate(ts_obj = map(data, get_ts_obj))

# cross-validate baseline models on each key (consider parallelizing)
train_by_key <- train_by_key %>%
  mutate(naive_errors = map(ts_obj, tsCV, forecastfunction = naive, h = 3),
         meanf_errors = map(ts_obj, tsCV, forecastfunction = meanf, h = 3),
         snaive_errors = map(ts_obj, tsCV, forecastfunction = snaive, h = 3),
         drift_errors = map(ts_obj, tsCV, forecastfunction = rwf, drift = TRUE, h = 3))

# get performance metrics across horizon for each model
get_cv_metric <- function(errors = NULL, norm_const = 1, metric = 'rmse') {
  if (metric == 'mae'){
    cv_metric <- colMeans(abs(errors), na.rm = T)/norm_const
  } else if (metric == 'rmse'){
    cv_metric <- sqrt(colMeans(errors^2, na.rm = T))/norm_const
  } else {
    cv_metric <- NA
  }
}

get_metric_df <- function(data = NULL, model = NULL, metric = 'rmse', normalize = FALSE){
  if (normalize){
    norms <- map(data$data, function(x) mean(x$Weekly_Sales, na.rm = TRUE))
  } else {
    norms <- rep(1, times = nrow(data))
  }
  if (model == 'naive'){
    metric_df <- map2_dfr(data$naive_errors, norms, get_cv_metric, metric = metric)
  } else if (model == 'meanf'){
    metric_df <- map2_dfr(data$meanf_errors, norms, get_cv_metric, metric = metric)
  } else if (model == 'snaive'){
    metric_df <- map2_dfr(data$snaive_errors, norms, get_cv_metric, metric = metric)
  } else if (model == 'drift'){
    metric_df <- map2_dfr(data$drift_errors, norms, get_cv_metric, metric = metric)
  }
  metric_df <-  pivot_longer(data = metric_df, 
                                   cols = colnames(metric_df), 
                                   names_to = 'horizon', 
                                   values_to = 'metric') %>%
      group_by(horizon) %>%
      summarise(median = median(metric, na.rm = TRUE),
                lower = quantile(metric, probs = 0.1, na.rm = TRUE),
                upper = quantile(metric, probs = 0.9, na.rm = TRUE)) %>%
      mutate(model = model,
             metric = metric)
}

suppressMessages({
  naive_rmse_df <- get_metric_df(data = train_by_key, model = 'naive', metric = 'rmse')
  snaive_rmse_df <- get_metric_df(data = train_by_key, model = 'snaive', metric = 'rmse')
  meanf_rmse_df <- get_metric_df(data = train_by_key, model = 'meanf', metric = 'rmse')
  drift_rmse_df <- get_metric_df(data = train_by_key, model = 'drift', metric = 'rmse')
  naive_mae_df <- get_metric_df(data = train_by_key, model = 'naive', metric = 'mae')
  snaive_mae_df <- get_metric_df(data = train_by_key, model = 'snaive', metric = 'mae')
  meanf_mae_df <- get_metric_df(data = train_by_key, model = 'meanf', metric = 'mae')
  drift_mae_df <- get_metric_df(data = train_by_key, model = 'drift', metric = 'mae')
  
  naive_rmse_norm_df <- get_metric_df(data = train_by_key, model = 'naive', metric = 'rmse', normalize = TRUE) %>%
    mutate(metric = 'normalized rmse')
  snaive_rmse_norm_df <- get_metric_df(data = train_by_key, model = 'snaive', metric = 'rmse', normalize = TRUE) %>%
    mutate(metric = 'normalized rmse')
  meanf_rmse_norm_df <- get_metric_df(data = train_by_key, model = 'meanf', metric = 'rmse', normalize = TRUE) %>%
    mutate(metric = 'normalized rmse')
  drift_rmse_norm_df <- get_metric_df(data = train_by_key, model = 'drift', metric = 'rmse', normalize = TRUE) %>%
    mutate(metric = 'normalized rmse')
  naive_mae_norm_df <- get_metric_df(data = train_by_key, model = 'naive', metric = 'mae', normalize = TRUE) %>%
    mutate(metric = 'normalized mae')
  snaive_mae_norm_df <- get_metric_df(data = train_by_key, model = 'snaive', metric = 'mae', normalize = TRUE) %>%
    mutate(metric = 'normalized mae')
  meanf_mae_norm_df <- get_metric_df(data = train_by_key, model = 'meanf', metric = 'mae', normalize = TRUE) %>%
    mutate(metric = 'normalized mae')
  drift_mae_norm_df <- get_metric_df(data = train_by_key, model = 'drift', metric = 'mae', normalize = TRUE) %>%
    mutate(metric = 'normalized mae')
  
  metric_df <- rbind(naive_rmse_df, snaive_rmse_df, meanf_rmse_df, drift_rmse_df,
                     naive_rmse_norm_df, snaive_rmse_norm_df, meanf_rmse_norm_df, drift_rmse_norm_df,
                     naive_mae_df, snaive_mae_df, meanf_mae_df, drift_mae_df,
                     naive_mae_norm_df, snaive_mae_norm_df, meanf_mae_norm_df, drift_mae_norm_df)
  metric_df$metric <- factor(metric_df$metric, ordered = TRUE, levels = c('rmse', 'mae', 'normalized rmse', 'normalized mae'))
})

#plot performance metrics across horizon by model
ggplot(data = metric_df, 
       aes(x = horizon, 
           y = median,
           group = model, 
           color = model)
       ) +
  geom_point() +
  facet_wrap(~metric, scales = "free", nrow = 2) +
  xlab('horizon (weeks)') +
  theme(aspect.ratio = 1)

```
For these relatively short 3 week forecasts, the seasonal naive model seems to do the worst. It may do better for longer forecasts. The drift model does okay at one step prediction, but performance quickly degrades with increasing horizon. Perhaps unsurprisingly, the naive model performs best on one step prediction, and degrades slightly less with increasing horizon. The meanf model also performs well and is more stable across horizons. It seems the best option might be to choose the naive model at short horizons (i.e., h = 1 or 2) and the meanf model at longer horizons (i.e., h = 3).

### Cross-validate Prophet
```{r}
# create nested data frame of full training data by key
train_by_key <- train %>%
  group_by(Primary_Key) %>%
  nest

# create holidays argument
num_christmas <- length(unique(train$Date[train$IsChristmas])) + length(unique(test$Date[test$IsChristmas]))
num_thanksgiving <- length(unique(train$Date[train$IsThanksgiving])) + length(unique(test$Date[test$IsThanksgiving]))
num_laborday <- length(unique(train$Date[train$IsLaborDay])) + length(unique(test$Date[test$IsLaborDay]))
num_superbowl <- length(unique(train$Date[train$IsSuperBowl])) + length(unique(test$Date[test$IsSuperBowl]))
num_easter <- length(unique(train$Date[train$IsEaster])) + length(unique(test$Date[test$IsEaster]))
holidays <- data.frame(holiday = c(rep('Christmas',num_christmas),
                                   rep('Thanksgiving', num_thanksgiving),
                                   rep('LaborDay', num_laborday),
                                   rep('SuperBowl', num_superbowl),
                                   rep('Easter', num_easter)),
                       ds = as.Date(c(unique(train$Date[train$IsChristmas]), unique(test$Date[test$IsChristmas]),
                                      unique(train$Date[train$IsThanksgiving]), unique(test$Date[test$IsThanksgiving]),
                                      unique(train$Date[train$IsLaborDay]), unique(test$Date[test$IsLaborDay]),
                                      unique(train$Date[train$IsSuperBowl]), unique(test$Date[test$IsSuperBowl]),
                                      unique(train$Date[train$IsEaster]), unique(test$Date[test$IsEaster]))),
                       lower_window = -14,
                       upper_window = 14)

# get prophet object for each key
get_prophet_obj <- function(df, holidays, growth = 'linear') {
  pb$tick()$print()
  if (nrow(df) > 56){
    #prepare data
    df <- df %>% rename(ds = Date) %>% rename(y = Weekly_Sales) 
    prophet_obj <- prophet(growth = 'linear',
                           yearly.seasonality = 6,
                           weekly.seasonality = FALSE,
                           daily.seasonality = FALSE,
                           seasonality.mode = "additive",
                           holidays = holidays,
                           fit = FALSE)
    prophet_obj <- add_seasonality(prophet_obj, name='monthly', period=30.5, fourier.order=1)
    prophet_obj <- fit.prophet(prophet_obj, df = df)
  } else {
   prophet_obj <- NA 
  }
}
print('fitting initial prophet models:')
pb <- progress_estimated(nrow(train_by_key))
suppressMessages({
  train_by_key <- train_by_key %>% 
    mutate(prophet_obj = map(data, get_prophet_obj, holidays = holidays, growth = 'linear'))
})

# cross-validate prophet on each key (consider parallelizing)
prophet_cv <- function(prophet_obj, horizon = 3) {
  pb$tick()$print()
  num_weeks <- nrow(prophet_obj$history)
  initial <- as.numeric(prophet_obj$history$Week[num_weeks - horizon])
  period <- 150
  cv <- cross_validation(prophet_obj, horizon = horizon, period = period, units = 'weeks')
}
print('cross-validating prophet models:')
pb <- progress_estimated(sum(!is.na(train_by_key$prophet_obj)))
suppressMessages({
  prophet_by_key <- train_by_key %>%
    filter(!is.na(prophet_obj)) %>%
    mutate(prophet_cv = map(prophet_obj, prophet_cv)) %>%
    mutate(prophet_metrics = map(prophet_cv, performance_metrics, rolling_window = 0))
})

# gather performance metrics
metric_df <- prophet_by_key %>% 
  select(Primary_Key, prophet_metrics) %>%
  unnest(prophet_metrics) %>%
  group_by(horizon) %>%
  summarise(rmse = sqrt(mean(rmse^2, na.rm = TRUE)),
            mae = mean(mae, na.rm = TRUE),
            mape = mean(mape, na.rm = TRUE),
            coverage = mean(coverage, na.rm = TRUE),
            .groups = 'drop') %>%
  pivot_longer(cols = c('rmse', 'mae', 'mape', 'coverage'), 
               names_to = 'metric', 
               values_to = 'value') %>%
  mutate(horizon = as.numeric(horizon)/7)

#plot performace metrics
ggplot(data = metric_df, aes(x = horizon, y = value)) +
  geom_point() +
  facet_wrap(~metric, scales = "free", nrow = 2) +
  xlab('horizon (weeks)') +
  theme(aspect.ratio = 1)
```


